Article Title

### 2013-10-02 sections/Regularization.tex
minor

\subsection*{Regularization}
Under many loss functions\footnote{
The strict equality in Eq.~\ref{eq:bias-variance} does not hold under the loss function in Eq.~\ref{eq:loss}. 
However, the equality does hold for its close cousin, Stein's \emph{entropy loss}, which only differs by the order of its arguments and a constant offset: $\mathcal L_s(\hat\Sigma,\Sigma) \equiv \loss{\Sigma,\hat\Sigma} - \loss{\Sigma,\Sigma}$. 
This defficiency presents no difficulty because we minimize the risk directly, without assessing the two error components individually. 
The bias-variance decomposition is presented here to motivate the use of regularization.}, 
the estimator's risk can be decomposed as the sum
\begin{equation}\label{eq:bias-variance}
    r = b + \varepsilon
\end{equation}
of \emph{approximation error} (``bias'' or systematic error)
\begin{equation}
   b = \loss{\bar\Sigma,\Sigma}
\end{equation}
and \emph{estimation error} (``variance'') 
\begin{equation}
   \varepsilon = \E[\hat\Sigma]{\loss{\hat\Sigma, \bar\Sigma}}
\end{equation}
where $\bar\Sigma = \E{\hat\Sigma}$ is the expected value of the estimate.

The unbiased estimator $\hat\Sigma_0$ makes $\bar\Sigma=\Sigma$ and thereby minimizes the approximation error, but may be excessively susceptible to sample noise and result in high estimation error.

>>>>

\subsection*{Regularization}
Under many loss functions\footnote{
The strict equality in Eq.~\ref{eq:bias-variance} does not hold under the loss function in Eq.~\ref{eq:loss}. 
However, the equality does hold for its close cousin, Stein's \emph{entropy loss}, which only differs by the order of its arguments and a constant offset: $\mathcal L_s(\hat\Sigma,\Sigma) \equiv \loss{\Sigma,\hat\Sigma} - \loss{\Sigma,\Sigma}$. 
This defficiency presents no difficulty because we minimize the risk directly, without assessing the two error components individually. 
The bias-variance decomposition is presented here to motivate the use of regularization.}, 
the risk can be decomposed as the sum
\begin{equation}\label{eq:bias-variance}
    r = b + \varepsilon
\end{equation}
of \emph{approximation error} (``bias'' or systematic error)
\begin{equation}
   b = \loss{\bar\Sigma,\Sigma}
\end{equation}
and \emph{estimation error} (``variance'') 
\begin{equation}
   \varepsilon = \E[\hat\Sigma]{\loss{\hat\Sigma, \bar\Sigma}}
\end{equation}
where $\bar\Sigma = \E{\hat\Sigma}$ is the expected value of the estimate.

The unbiased estimator $\hat\Sigma_0$ makes $\bar\Sigma=\Sigma$ and thereby minimizes approximation error, but may be excessively susceptible to sample noise and result in high estimation error.

### 2013-10-02 sections/Simulation.tex
minor

\subsection*{In simulation, estimator selection `recognizes' the covariance structure}
\input{sections/Figure3.tex}

>>>>

\subsection*{Simulation: estimators perform better when their target matches the low-dimensional structure of the true covariance matrix}
\input{sections/Figure3.tex}

A common misconception about regularization is that its effect depends on accurate prior knowlege about the structure of the data. However, substantial improvement can be attained by shrinking the unbiased estimate toward an arbitrary target as long as the target is less variable than the unbiased estimator.  This unintuitive phenomenon is known as \emph{Stein's paradox} \cite{Efron:1977}.  The more accurate description of regularization is the as the optimal tradeoff between estimation and approximation error, the so-called ``bias-variance tradeoff'' as described above.

Therefore, taken in isolation, the fact that a given regularized estimator improved the estimate should not be interpreted to suggest that its target estimate has the same low-dimensional structure as the data generating process.   However, when multiple estimators are compared against each other, the ones whose target estimate can closely approximate the true value with the smallest number of parameters will be able to reduce the estimation error with mininimum increases in approximation error when compared against other estimators whose targets cannot consistenly approximate the true covariance matrix.
